MP MetaAnalysis

### 2018-06-21 Paper_Analyses.Rmd
ICIS_2018_poster_prep

The database contains data from `r length(unique(dat$short_cite))` papers consisting of data from `r sum(sum_dat$n_1)` infants. In the tables below, we provide more descriptive information.

@@

@@

@@

## Number of features
Size of mispronunciation, measured in features changed

@@

db_ET_MPf = db_ET_MP %>%
  filter(n_feature != "1-3" & n_feature != "1-2" & n_feature != "2-3")

@@

@@

@@

@@

@@

@@

### Plot Language Family by MP type: Consonant, Vowel, or Tone?
```{r PlotCVEffect_Lang}

@@

### Distractor Familiarity with age moderator, subset to same age range

```{r DistractorTypeAgeRangeSubset}

min_age <- min(dat[dat$object_pair=="familiar_novel",]$mean_age_1)
max_age <- max(dat[dat$object_pair=="familiar_novel",]$mean_age_1)

@@

@@

min_age<-min(dat[dat$object_pair=="familiar_novel",]$mean_age_1)
max_age <- max(dat[dat$object_pair=="familiar_novel",]$mean_age_1)

@@

dat_age$condition_label = ifelse(dat_age$condition==1, "correct", "MP")
dat_age$dist_code <- ifelse(dat_age$object_pair == "familiar_familiar", "familiar", "unfamiliar")

p <- ggplot(dat_age, aes(dist_code, g_calc, color = condition_label)) + 
  geom_boxplot() + 
  #geom_line(y= 0, linetype="dotted") + 
  #geom_smooth(method = "lm", formula = y ~ log(x), aes(weight=weights_g)) + 
  scale_color_manual(values=wes_palette(name="Darjeeling"))+
  theme_bw()+
  theme(text = element_text(size=25),
        legend.title = element_blank(),
        legend.position = "bottom") + 
  xlab("Distractor Familiarity") + 
  ylab("Effect size Hedges' g")
p

@@

@@

### Plot Position of Mispronunciation
```{r PlotPositionEffect}

@@

### Plot Distractor Overlap

@@

### Plot Language Effect
```{r PlotLanguageEffect}

>>>>

The database contains data from `r length(unique(dat$short_cite))` papers. In the tables below, we provide more descriptive information.

@@

## Number of unique infants

```{r DescriptivesInfnum, echo = FALSE}

infnum_info <- dat[,c("unique_ID", "same_infant", "expt_num", "n_1")]
infnum_info <- unique(infnum_info)

number_of_infants <- sum(infnum_info$n_1)

The database contains data from `r number_of_infants` unique infants.

## Number of unique experimental conditions

```{r DescriptivesExpCond, echo = FALSE}

condnum_info <- dat[,c("unique_ID", "same_infant", "expt_num", "expt_condition")]
condnum_info <- unique(condnum_info)

number_of_cond <- nrow(condnum_info)

The database contains data from `r number_of_cond` unique experimental conditions

@@

## Plotting Mispronunciation Effect

@@

## Number of Features Changed

### Number of features

Size of mispronunciation, measured in features changed

@@

db_ET_MPf  <- subset(db_ET_MP, n_feature == "0" | n_feature == "1" |
                n_feature == "2" | n_feature == "3")

@@

### Number of features subset to age range
Size of mispronunciation, measured in features changed

```{r NFeatures_subset}

mf <- subset(dat_f, n_feature == "3")
min_age <- min(mf$mean_age_1)
max_age <- max(mf$mean_age_1)

dat_fage= dat_f%>%
  filter(mean_age_1>=min_age&mean_age_1<=max_age)

#rma_NFeatures <- rma.mv(g_calc, g_var_calc, mods = ~as.ordered(n_feature), data = db_ET_MP, random = ~collapse | short_cite)
rma_NFeatures_agesub <- rma.mv(g_calc, g_var_calc, mods = ~as.factor(n_feature), data = dat_f, random = ~collapse | short_cite)

summary(rma_NFeatures_agesub)

@@

### Features changed with age moderator, subset to same age range

```{r FeatureAgeRangeSubset}

mf <- subset(dat_f, n_feature == "3")
min_age <- min(mf$mean_age_1)
max_age <- max(mf$mean_age_1)

dat_fage= dat_f%>%
  filter(mean_age_1>=min_age&mean_age_1<=max_age)

rma_FeatureAgeS <- rma.mv(g_calc, g_var_calc, mods = ~age.C*as.factor(n_feature), data = dat_fage, random = ~ collapse | short_cite)

summary(rma_FeatureAgeS)

#rma_FeatureS <- rma.mv(g_calc, g_var_calc, mods = ~condition*as.factor(n_feature), data = dat_fage, random = ~ collapse | short_cite)

#summary(rma_FeatureS)

## Plotting number of Features Changed

@@

```
### Plot number of Features subsetted for age

```{r PlotFeatEffect_agesubset}

mf <- subset(dat_f, n_feature == "3")
min_age <- min(mf$mean_age_1)
max_age <- max(mf$mean_age_1)

dat_fage= dat_f%>%
  filter(mean_age_1>=min_age&mean_age_1<=max_age)

dat_fage$feat_cat <- ifelse(dat_fage$n_feature == 1, "1-feature",
                         ifelse(dat_fage$n_feature == 2, "2-feature",
                                ifelse(dat_fage$n_feature == 3, "3-feature",
                                       ifelse(dat_fage$n_feature == 0, "correct", "none"))))

dat_fage <- subset(dat_fage, feat_cat != "none")

dat_fage$Features_changed <- factor(dat_fage$feat_cat, levels = c("correct", "1-feature", "2-feature", "3-feature"))

p <- ggplot(dat_fage, aes(mean_age_1/30.44, g_calc, color = Features_changed)) + 
  geom_point(aes(size = weights_g, shape = Features_changed),show.legend=FALSE) + 
  #facet_grid(.~type_feature)+
    scale_colour_manual(values=cbPalette)+
  geom_line(y= 0, linetype="dotted") + 
  geom_smooth(method = "lm", formula = y ~ log(x), aes(weight=weights_g)) + 
  apatheme +
  theme(legend.title = element_blank(),
        legend.position = "bottom") + 
  xlab("Age in months") + 
  ylab("Effect size Hedges' g")
p

ggsave("figures/AgeEffect_log_feat_agesub.jpg", p)

### Plot number of Features subsetted for age Boxplot

```{r PlotFeatEffect_agesubset_boxplot}

mf <- subset(dat_f, n_feature == "3")
min_age <- min(mf$mean_age_1)
max_age <- max(mf$mean_age_1)

dat_fage= dat_f%>%
  filter(mean_age_1>=min_age&mean_age_1<=max_age)

dat_fage$feat_cat <- ifelse(dat_fage$n_feature == 1, "1-feature",
                         ifelse(dat_fage$n_feature == 2, "2-feature",
                                ifelse(dat_fage$n_feature == 3, "3-feature",
                                       ifelse(dat_fage$n_feature == 0, "correct", "none"))))

dat_fage <- subset(dat_fage, feat_cat != "none")

dat_fage$Features_changed <- factor(dat_fage$feat_cat, levels = c("correct", "1-feature", "2-feature", "3-feature"))

p <- ggplot(dat_fage, aes(Features_changed, g_calc, fill = Features_changed)) + 
  geom_boxplot() + 
  #geom_smooth(method = "lm", formula = y ~ log(x), aes(weight=weights_g)) + 
  scale_fill_manual(values=cbPalette)+
  apatheme +
  theme(text = element_text(size=25),
        legend.title = element_blank(),
        legend.position = "none",
        axis.title.x = element_blank()) + 
  #xlab("Number of Features Changed") + 
  geom_hline(yintercept = 0, linetype="dotted") + 
  ylab("Effect size Hedges' g")

ggsave("figures/AgeEffect_log_feat_agesub_noage.jpg", p)

@@

### Type of MP: Vowel, consonant, or tone

@@

## Plotting MP type: Consonant, Vowel, or Tone?

@@

### Plot Language Family by MP type: Consonant, Vowel, or Tone?

```{r PlotCVEffect_Lang}

@@

### Distractor Familiarity with condition moderator, subset to same age range

```{r DistractorTypeAgeRangeSubset_condition}

mf <- subset(dat, object_pair=="familiar_novel")
min_age <- min(mf$mean_age_1)

mf <- subset(dat, object_pair=="familiar_familiar")
max_age <- max(mf$mean_age_1)

dat_age= dat%>%
  filter(mean_age_1>=min_age&mean_age_1<=max_age)

rma_DistractorAgeS <- rma.mv(g_calc, g_var_calc, mods = ~condition*as.factor(object_pair), data = dat_age, random = ~ collapse | short_cite)

### Distractor Familiarity with age and condition moderator, subset to same age range

```{r DistractorTypeAgeRangeSubset_agecondition}

mf <- subset(dat, object_pair=="familiar_novel")
min_age <- min(mf$mean_age_1)

mf <- subset(dat, object_pair=="familiar_familiar")
max_age <- max(mf$mean_age_1)

dat_age= dat%>%
  filter(mean_age_1>=min_age&mean_age_1<=max_age)

@@

### Plotting Distractor Familiarity

@@

mf <- subset(dat, object_pair=="familiar_novel")
min_age <- min(mf$mean_age_1)

mf <- subset(dat, object_pair=="familiar_familiar")
max_age <- max(mf$mean_age_1)

@@

dat_age$condition_label = ifelse(dat_age$condition==1, "correct", "mispronunciation")
dat_age$dist_code <- ifelse(dat_age$object_pair == "familiar_familiar", "Familiar Distractor", "Unfamiliar Distractor")

p <- ggplot(dat_age, aes(condition_label, g_calc, fill = condition_label)) + 
  geom_boxplot() + 
  facet_grid(.~dist_code) +
  #geom_smooth(method = "lm", formula = y ~ log(x), aes(weight=weights_g)) + 
  scale_fill_manual(values=cbPalette)+
  apatheme +
  theme(text = element_text(size=25),
        legend.title = element_blank(),
        legend.position = "bottom",
        axis.title.x = element_blank(),
        axis.text.x = element_blank(),
        axis.ticks.x = element_blank()) + 
  #xlab("Number of Features Changed") + 
  geom_hline(yintercept = 0, linetype="dotted") + 
  ylab("Effect size Hedges' g")

@@

### Plot Distractor Familiarity by age subsetted for age

```{r PlotDistFam}

mf <- subset(dat, object_pair=="familiar_novel")
min_age <- min(mf$mean_age_1)

mf <- subset(dat, object_pair=="familiar_familiar")
max_age <- max(mf$mean_age_1)

dat_fage= dat%>%
  filter(mean_age_1>=min_age&mean_age_1<=max_age)

dat_fage$dist_fam <- ifelse(dat_fage$object_pair == "familiar_novel", "Novel Distractor", "Familiar Distractor")

p <- ggplot(dat_fage, aes(mean_age_1/30.44, g_calc, color = condition_label)) + 
  geom_point(aes(size = weights_g, shape = dist_fam),show.legend=FALSE) + 
  facet_grid(.~dist_fam)+
    scale_colour_manual(values=cbPalette)+
  geom_line(y= 0, linetype="dotted") + 
  geom_smooth(method = "lm", formula = y ~ log(x), aes(weight=weights_g)) + 
  apatheme +
  theme(legend.title = element_blank(),
        legend.position = "bottom") + 
  xlab("Age in months") + 
  ylab("Effect size Hedges' g")
p

ggsave("figures/AgeEffect_log_DistFam_agesub.jpg", p)

@@

## Plotting Position of Mispronunciation
```{r PlotPositionEffect}

@@

## Plotting Distractor Overlap

@@

## Plotting Language Effect
```{r PlotLanguageEffect}
